HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-05-16 tmlr_submission/hermes_paper_revision/answers_reviews.tex

\documentclass[10pt]{article} % For LaTeX2e
\usepackage{tmlr}
% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{tmlr}
% To de-anonymize and remove mentions to TMLR (for example for posting to preprint servers), instead use the following:
%\usepackage[preprint]{tmlr}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
\input{math_commands.tex}

\usepackage{hyperref}
\usepackage{url}
\usepackage{amssymb,amsmath,amsthm}
\usepackage[pdftex]{graphicx}

\title{HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series}

% Authors must not appear in the submitted version. They should be hidden
% as long as the tmlr package is used without the [accepted] or [preprint] options.
% Non-anonymous submissions will be rejected without review.

\author{\name \'Etienne David \email etienne.david@heuritech.com \\
      \addr SAMOVAR, Télécom SudParis,\\
      Institut Polytechnique de Paris, 91120 Palaiseau, France
      \AND
      \name Jean Bellot \email jean.bellot@heuritech.com \\
      \addr Heuritech, \\
      6 Rue de Braque, 75003 Paris
      \AND
      \name Sylvain Le Corff \email sylvain.lecorff@gmail.com\\
      \addr LPSM, \\
      Sorbonne Université, UMR CNRS 8001, 75005, Paris
      }

% The \author macro works with any number of authors. Use \AND 
% to separate the names and addresses of multiple authors.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\def\month{01}  % Insert correct month for camera-ready version
\def\year{2023} % Insert correct year for camera-ready version
\def\openreview{\url{https://openreview.net/forum?id=XXXX}} % Insert correct link to OpenReview for camera-ready version

\begin{document}

\maketitle

We would like to thank the reviewers and the associate editor for their constructive feedback, and their appreciation of the paper. We have carefully considered all the comments listed by the reviewers and we proposed a revision of the paper accordingly. You can find below an overview of the major modifications of the manuscript followed by detailed responses to the reviewers.

\section*{Major changes}

\section*{Reviewer 1}

\begin{itemize}
	\item {\em ``The paper does not provide a clear motivation or literature review for the choice of per-time-series models.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper could benefit from a more detailed discussion of the limitations of the proposed approach and potential avenues for future work.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper could also benefit from a more thorough comparison with existing methods, including a discussion of their strengths and weaknesses in relation to the proposed approach.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should provide a clear motivation or literature review for the choice of per-time-series models.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should explain why exponential smoothing and TBATS are chosen as the predictors, and how they compare to other possible choices such as ARIMA or HMM.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should compare with more existing methods.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should explain how HERMES handles different types of time series, such as stationary, non-stationary, seasonal, or sporadic.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should discuss the potential positive and negative impacts of the proposed model and dataset on the society and the environment.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should address the privacy and consent issues of using social media images and data to construct the fashion dataset and the weak signals.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should explain how the data is collected, processed, and anonymized, and what are the ethical and legal implications of this process.''} \medskip
	\textbf{Author response:} \\

	\item {\em ``The paper should also acknowledge the potential risks or biases of using social media data to represent fashion trends, such as cultural diversity, inclusivity, or sustainability.''} \medskip
	\textbf{Author response:} \\	
\end{itemize}

\section*{Reviewer 2}

\begin{itemize}
	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\		
\end{itemize}

\subsection*{Reviewer 3}

\begin{itemize}
	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\

	\item {\em ``''} \medskip
	\textbf{Author response:} \\		
\end{itemize}

\end{document}

### 2023-05-19 tmlr_submission/hermes_paper_revision/hermes_paper.tex
update revision with new results

In this paper, we consider an emerging time series forecasting application referred to as {\em fashion trends prediction}. In fashion and retails industries, accurately anticipating consumers' needs is vital and wrong decisions can lead to massive wastes. With the explosion of social network and the recent advances in image recognition, it is possible to translate the visibility of fashion items on social media over time into time series. Consequently, models and algorithms can be trained to accurately anticipate and predict consumer behaviour. In \citet{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality. However, only 3 years of historical data is available (144 data points) that may not be sufficient for some statistical approaches. In \citet{ma2020}, another dataset is presented gathering 8000 fashion sequences with an historical available data  increased to 5 years. Nevertheless, only 120 values are available for each fashion time series and the overall volume remains low for a large part of the sequences resulting in a lot of noise and no clear patterns. In this paper, we propose a new fashion dataset overcoming the weaknesses of the two previous ones. Based on cutting-edge image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019. This dataset has very appealing properties:  all time series have the same length (261 data points), there is no missing value and there is no sparse time series even for niche trends. Concerning fashion dynamics, some of them appear to be really volatile with nonlinear changes of dynamics resulting from the emergence of new tendencies. In this context, understanding early signals of the apparition of a trend is one of the key to accurately forecast the future of the fashion. Consequently, the originality of our dataset comes from the fact that additional external weak signals are introduced. With our fashion expertise, we detected several groups of highly influential fashion users. Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on a sub-category of users. They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal. Exploring this new way of representing fashion, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.

@@

Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals. This new architecture is decomposed  into two parts: local predictors and a global corrector.  First, a per-time-series parametric statistical model is trained on each sequence. Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models. The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.

The paper is organized as follows. Section~\ref{sec:dataset} presents the new fashion dataset provided with this article. Then, the proposed forecasting approach HERMES is presented in Section~\ref{sec:hybrid}. Section~\ref{sec:exp} describes the model results and comparisons with several benchmarks on the 2 different use cases: the fashion dataset and the M4 competition weekly dataset. Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.

@@

\subsection{Per-time-series predictors}
%The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past. 
For all $1\leqslant n \leqslant N$, we note $\stat^n(.;\statparam^n)$ the $n$-th parametric model of the $n$-th sequence where $\statparam^n$ are  unknown parameters. Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{pred,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
\begin{equation}
    \label{eq:predictors}
    \tspred^{pred,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i\,.
\end{equation}
During the M4 competition, the hybrid model of \citet{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice leads to poor results and instability. In this paper, a more general framework able to deal with any kind of per-time-series models is provided. In Section~\ref{sec:exp}, two versions of our framework are proposed. The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020} and the second one uses a TBATS model \citep{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.

%In the specific application of fashion trends prediction, two main forms of standard weaknesses were detected and defined for univariate parametric forecasts. The first one is a weakness of definition, when the model is not well defined for its forecasting task. For instance, an additive model provides good predictions on time series with additive seasonality but fails at handling multiplicative seasonalities. The second form, harder to detect and correct, is the weakness of information. 
For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In some cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that the exact influence of external variables on the main signal is mostly unknown. This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.

@@

As benchmarks, several widespread statistical methods and deep learning approaches were selected. Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats}, for each time series, predictions are computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}. The forecast of the \textit{snaive} method is only the repetition of the last past period. The \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component. The \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model. The \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} uses a trigonometrical seasonality. Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters. A complete description and references for these models can be found in \citet{hyndman2020}. As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.
Two versions of HERMES are proposed. They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice. Moreover, two versions with the inclusion of the weak signals (ws) are proposed. They are referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}. In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.

@@

Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings. Regarding \textit{hermes-ets},   although it is very similar to the baseline \citet{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.

Models using our weak signals perform similarly as without-weak-signals models for the MASE.  Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends. Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.

\begin{table}
  \caption{Results summary on the 10000ts Fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textit{thetam}  && 0.844 && -&&& 0.482 && - &\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& \textbf{0.510} && 0.005 &\\
  \end{tabular}
\label{tab:metricresults}
\end{table}

@@

\textbf{Size of the dataset. } In addition to the results on the whole fashion dataset, the robustness of the HERMES model is analyzed when it is trained on smaller datasets. Two experiments are performed on a sub sample of respectively 1000 and 100 randomly selected time series. Results are given in Table~\ref{tab:1000metricresults}. The hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets. 
We can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases. On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms the \textit{lstm}. Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require large amounts of data to do so. By contrast, the HERMES approach can rely on its first statistical part and consequently needs less data to be trained and to obtain interesting performance.

\begin{table}
  \caption{Results summary on the 1000 time series and 100 time series Fashion dataset. The MASE average on all the time series is computed. For the two approaches using a neural network, 10 models with different seeds are trained. the mean and the standard deviation of the 10 results are displayed.}
 \centering
 \resizebox{0.8\textwidth}{!}{ 
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{1000 time series Fashion dataset}\vspace{0.5cm} \\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	 \hline
	 &&& \\
     \textit{snaive} && 0.871 & - \\
     \textit{thetam}  && 0.849 & - \\
     \textit{arima} && 0.821 & - \\
     \textit{ets} && 0.801 & - \\
     \textit{stlm} && 0.765 & - \\
     \textit{lstm} && 0.740 & 0.007 \\
     \textit{tbats} && 0.734 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
  \end{tabular}\hspace{1cm}
\vspace{.2cm}

  \begin{tabular}{l||llll}
   \multicolumn{4}{c}{100 ts Fashion dataset}\vspace{0.5cm} \\
   &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	\hline
	 &&& \\
     \textit{snaive} && 0.876 & - \\
     \textit{thetam}  && 0.823 & - \\
     \textit{arima} && 0.814 & - \\
     \textit{ets} && 0.785 & - \\
     \textit{lstm} && 0.767 & 0.045 \\
     \textit{stlm} && 0.742 & - \\
     \textit{tbats} && 0.745 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.739} & 0.003 \\
  \end{tabular}
 }
\label{tab:1000metricresults}
\end{table}

@@

\appendix
\section{M4 weekly dataset, Ensembling training and results}

>>>>

In this paper, we consider an emerging time series forecasting application referred to as {\em fashion trends prediction}. In fashion and retails industries, accurately anticipating consumers' needs is vital and wrong decisions can lead to massive wastes. With the explosion of social network and the recent advances in image recognition, it is possible to translate the visibility of fashion items on social media over time into time series. Consequently, models and algorithms can be trained to accurately anticipate and predict consumer behaviour. In \citet{ma2020}, a  dataset is provided using social media pictures and an image recognition framework to detect several clothes: 2000 fashion time series are proposed with a weekly seasonality. However, only 3 years of historical data is available (144 data points) that may not be sufficient for some statistical approaches. In \citet{ma2020}, another dataset is presented gathering 8000 fashion sequences with an historical available data  increased to 5 years. Nevertheless, only 120 values are available for each fashion time series and the overall volume remains low for a large part of the sequences resulting in a lot of noise and no clear patterns. In this paper, we propose a new fashion dataset overcoming the weaknesses of the two previous ones. Based on cutting-edge image recognition algorithms \citep{ren2015,chollet2017}, we built a large fashion dataset containing \numberts\ weekly sequences of fashion trends on social media with 5 years of historical data from 01-01-2015 to 30-12-2019. This dataset has very appealing properties:  all time series have the same length (261 data points), there is no missing value and there is no sparse time series even for niche trends. Concerning fashion dynamics, some of them appear to be really volatile with nonlinear changes of dynamics resulting from the emergence of new tendencies. In this context, understanding early signals of the apparition of a trend is one of the key to accurately forecast the future of the fashion. Consequently, the originality of our dataset comes from the fact that additional external weak signals are introduced. With our fashion expertise, we detected several groups of highly influential fashion users. Analyzing their specific behaviours on social media, we associate with each time series an external weak signal representing the same fashion trends on \textcolor{gray}{a} \textcolor{orange}{this} sub-category of users. They are called weak signals because they are often alerts or events that are too sparse, or too incomplete to allow on their own an accurate estimation of their impact on the prediction of the target signal. Exploring this new way of representing fashion, we aim at designing a model able to deal with such a large dataset, leveraging  complex external weak signals and finally providing the most accurate forecasts.

@@

Following this work, we present in this paper HERMES, a new hybrid recurrent model for time series forecasting with inclusion of external signals. This new architecture is decomposed  into two parts: \textcolor{gray}{local predictors and a global corrector. First, a per-time-series parametric statistical model is trained on each sequence. Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} \textcolor{orange}{i) First, a per-time-series parametric statistical model is trained on each sequence. ii) Then, a global recurrent neural network is trained to evaluate and correct the forecast weaknesses of the first collection of models.} The external weak signals reveal the real potential of the hybrid approach: a global neural network, able to leverage large amounts of heterogeneous data, deal with any kind of external weak signals, learn context and finally correct weaknesses and errors of parametric models.

The paper is organized as follows. Section~\ref{sec:dataset} presents the new fashion dataset provided with this article. Then, the proposed forecasting approach HERMES is presented in Section~\ref{sec:hybrid}. Section~\ref{sec:exp} describes the model results and comparisons with several benchmarks on \textcolor{gray}{the} 2 different use cases: the fashion dataset and the M4 competition weekly dataset. Finally, a general conclusion and some research perspectives are given in  Section~\ref{sec:conclusion}.

@@

\subsection{Per-time-series predictors}
%The time-series-specific predictors compute, for each sequence, a first $\lag$-ahead prediction based on the past. 
For all $1\leqslant n \leqslant N$, we note $\stat^n(.;\statparam^n)$ the $n$-th parametric model of the $n$-th sequence where $\statparam^n$ are  unknown parameters. Given the sequences $\{\ts^n_{1:T}\}_{1\leqslant n \leqslant N}$ and the estimated  parameters $\{\statparam^n\}_{1\leqslant n \leqslant N}$, the time-series-specific forecasts $\{\tspred^{pred,n}_{T+1:T+\lag|T}\}_{1\leqslant n \leqslant N}$ are, for all $n \in \{1,\ldots,N\}$, for all $i \in \{1,\ldots,\lag\}$,
\begin{equation}
    \label{eq:predictors}
    \tspred^{pred,n}_{T+i|T} = \stat^n(\ts^n_{1:T};\statparam^n)_i\,.
\end{equation}

During the M4 competition, the hybrid model of \citet{smyl2020} was based on a multiplicative exponential smoothing model as the time-series-specific predictor. However, on sporadic time series, this choice leads to poor results and instability. In this paper, a more general framework able to deal with any kind of per-time-series models is provided. \textcolor{orange}{Thus, the choice of the parametric model can be adjusted depending on the nature of the time series. The only limitation is the computation time. For instance, hidden Markov models or ARIMA models are powerfull parametric methodes but they are also computational expensive to fit. Choosing these approaches as per-time-series predictor may considerably slow the overall training process of the hybrid model. In Section~\ref{sec:exp}, three declinations of the hybrid framework are presented using different per-time-series predictors. The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020}, the second one use a method called Thetam as per-time-series predictor \citep{hyndman2020} and the last one uses a TBATS model \citep{alysha2011}.} \textcolor{gray}{In Section~\ref{sec:exp}, two versions of our framework are proposed. The first one is based on an  exponential smoothing as a reference similar to the baseline \citet{smyl2020} and the second one uses a TBATS model \citep{alysha2011} which provides better results as this parametric model includes  Fourier representations with time varying coefficients, and ARMA error correction.}

For non stationary time series, huge changes of behaviours are not always predictable using the past of the sequence. In some cases, these changes depend on external variables not considered by univariate parametric models. The difficulty is that the exact influence of external variables on the main signal is mostly unknown. This motivates the introduction of a global RNN trained on all time series and able to consider and leverage external signals.

@@

As benchmarks, several widespread statistical methods and deep learning approaches were selected. Using the R package \texttt{forecast} and the Python packages \texttt{statsmodels},  \texttt{tbats}, for each time series, predictions are computed with the following methods: \textit{snaive}, \textit{ets}, \textit{stlm}, \textit{thetam}, \textit{tbats} and \textit{auto.arima}. The forecast of the \textit{snaive} method is only the repetition of the last past period. The \textit{ets} model is an additive exponential smoothing with a level component and a seasonal component. The \textit{stlm} approach uses a multiplicative decomposition and models the seasonally adjusted time series with an exponential smoothing model. The \textit{Thetam} model decomposes the original signal in $\theta$-lines, predicts each one separately and recomposes them to produce the final forecast and \textit{tbats} uses a trigonometrical seasonality. Finally, \textit{auto.arima} is the R implementation of the ARIMA model with an automatic selection of the best parameters. A complete description and references for these models can be found in \citet{hyndman2020}. \textcolor{orange}{As deep learning apporaches, two recurrent neural networks are proposed. They are both composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52. The first one (called \textit{lstm}) has only access to the main signal while the second one (called \textit{lstm-ws}) has access to the main and the external signal.} \textcolor{gray}{As a deep learning approach, a full LSTM (\textit{lstm}) neural network composed of 3 LSTM layers of shape 50 and a final Dense layer of shape 52 is considered.}

\textcolor{orange}{
A strength of the proposed HERMES framework is that it can handle any kind of parametric model. This choice of per-time-series predictor is central in the approach and have to be done regarding the use case and the nature of the time series. Thus, three declinations of the HERMES approach are proposed on the Fashion dataset using different per-time-series predictors: Ets, Tbats and Thetam. They are called respectively \textit{hermes-ets}, \textit{hermes-tbats} and \textit{hermes-thetam} according to the per-time-series model choice. For each of them, a variation with the inclusion of the weak signals (\textit{-ws}) is presented.}
\textcolor{gray}{Two versions of HERMES are proposed. They are called respectively \textit{hermes-ets} and \textit{hermes-tbats} according to the per-time-series model choice. Moreover, two versions with the inclusion of the weak signals (ws) are proposed. They are referred to as \textit{hermes-ets-ws} and \textit{hermes-tbats-ws}. In order to provide a fair comparison, a \textit{lstm} with the weak signals named \textit{lstm-ws} is trained.}

@@

\textcolor{orange}{Considering the new HERMES approaches, all the different versions show consequent improvements regarding their per-time-series predictors in terms of MASE. \textit{Hermes-tbats} largely outperforms the two other declinations and all the benchmarks on the fashion dataset. This result highlight to important point of the proposed hybrid model: i) The final accuracy of the model is strongly impacted by the choice of per-time-series predictor ii) If the per-time-series predictor is well chosen regarding the nature of the time series, the resulting HERMES model can show impressive results and outperformance state-of-the-art approaches.}
\textcolor{gray}{Considering the new HERMES approach, \textit{hermes-tbats} and \textit{hermes-tbats-ws} slightly outperform the alternatives in terms of MASE and are stable across the different trainings. Regarding \textit{hermes-ets},   although it is very similar to the baseline \citet{smyl2020}, its accuracy remains low in comparison to the \textit{lstm} benchmark or HERMES using TBATS.}

\textcolor{orange}{Regarding the impact of the weak signals, improvement in terms of MASE remains low between methodes without and with the weak signal. However, an interesting improvement can be noted with the accuracy metric. Weak signals seem to grandtully help methods using them to better detect emerging and declining trends. Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} predictions and illustrates some Tbats weaknesses that can be corrected by the hybrid approach.}
\textcolor{gray}{
Models using our weak signals perform similarly as without-weak-signals models for the MASE.  Interestingly, weak signals significantly improve the accuracy in detecting emerging and declining trends. Figure~\ref{fig:examples} displays some examples of \textit{hermes-tbats} models and some weaknesses that can be corrected.}

\begin{table}
  \caption{Results summary on the 10000ts Fashion dataset. For each metric, the average on all our time series is computed. For approaches using neural networks, 10 models are trained with different seeds. The mean and the standard deviation of the 10 results are displayed.}
  \centering
  \begin{tabular}{l||lllll|lllll}
   &&\multicolumn{3}{c}{\textbf{MASE $\downarrow$}} &&& \multicolumn{3}{c}{\textbf{ACCURACY $\uparrow$}}&\\
    &&  \textit{mean}  && \textit{std} &&&  \textit{mean}  && \textit{std}& \\
	 \hline
	 &&&&&&&&&&\\
     \textit{snaive} && 0.881 && - &&& 0.357 && - &\\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.0.845} && \textcolor{orange}{-} &&& \textcolor{orange}{0.463} && \textcolor{orange}{-}\\
     \textit{arima} && 0.826 && -&&& 0.464 && - & \\
     \textit{ets} && 0.807 && -&&& 0.449 && - & \\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.786} && \textcolor{orange}{-} &&& \textcolor{orange}{0.485} && \textcolor{orange}{-}\\
     \textit{stlm} && 0.770 && -&&& 0.482 && - & \\
     \textit{hermes-ets-ws} && 0.769 && 0.005 &&& 0.501 && 0.007 &\\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} && \textcolor{orange}{0.003} &&& \textcolor{orange}{0.497} && \textcolor{orange}{0.005}\\
     \textcolor{orange}{\textit{hermes-thetam-ws}} && \textcolor{orange}{0.760} && \textcolor{orange}{0.004} &&& \textcolor{orange}{\textbf{0.520}} && \textcolor{orange}{0.01}\\
     \textit{hermes-ets} && 0.758 && 0.001 &&& 0.490 && 0.006 &\\
     \textit{tbats} && 0.745 && -&&& 0.453 && - & \\
     \textit{lstm-ws} && 0.728 && 0.004 &&& 0.500 && 0.008 &\\
     \textit{lstm} && 0.724 && 0.003 &&& 0.498 && 0.007 &\\
     \textit{hermes-tbats} && 0.715 && 0.002 &&& 0.488 && 0.008 &\\
     \textbf{\textit{hermes-tbats-ws}} && \textbf{0.712} && 0.004 &&& 0.510 && 0.005 &\\
  \end{tabular}
\label{tab:metricresults}
\end{table}

@@

\textbf{Size of the dataset. } In addition to the results on the whole fashion dataset, the robustness of the HERMES model is analyzed when it is trained on smaller datasets. Two experiments are performed on a sub sample of respectively 1000 and 100 randomly selected time series. Results are given in Table~\ref{tab:1000metricresults}. The hybrid framework \textit{hermes-tbats} achieves the best performance in terms of global accuracy on both datasets. We can note that the accuracy of the full neural network \textit{lstm} decreases when the dataset size decreases. On the small dataset of 100 time series, a local statistical model like \textit{tbats} or \textit{stlm} largely outperforms the \textit{lstm}. Providing sharp predictions from scratch is a complex task and high-dimensional recurrent neural networks require large amounts of data to do so. By contrast, the HERMES approach can rely on its first statistical part and consequently needs less data to be trained and to obtain interesting performance. \textcolor{orange}{We can nevertheless note that the gain brought by the error-corrector recurrent model decreases as the size of the dataset diminish.}

\begin{table}
  \caption{Results summary on the 1000 time series and 100 time series Fashion dataset. The MASE average on all the time series is computed. For the two approaches using a neural network, 10 models with different seeds are trained. the mean and the standard deviation of the 10 results are displayed.}
 \centering
 \resizebox{0.8\textwidth}{!}{ 
  \begin{tabular}{l||llll}
    \multicolumn{4}{c}{1000 time series Fashion dataset}\vspace{0.5cm} \\
    &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	 \hline
	 &&& \\
     \textit{snaive} && 0.871 & - \\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.837} & \textcolor{orange}{-} \\
     \textit{arima} && 0.821 & - \\
     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.801} & \textcolor{orange}{-} \\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.788} & \textcolor{orange}{-} \\
     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.768} & \textcolor{orange}{0.005} \\
     \textit{stlm} && 0.765 & - \\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.764} & \textcolor{orange}{0.004} \\
     \textit{lstm} && 0.740 & 0.007 \\
     \textit{tbats} && 0.734 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.719} & 0.002 \\
  \end{tabular}\hspace{1cm}
\vspace{.2cm}

  \begin{tabular}{l||llll}
   \multicolumn{4}{c}{100 ts Fashion dataset}\vspace{0.5cm} \\
   &&\multicolumn{2}{c}{\textbf{MASE}} \\
    &&  \textit{mean}  & \textit{std}  \\
	\hline
	 &&& \\
     \textit{snaive} && 0.876 & - \\
     \textcolor{orange}{\textit{thetam}} && \textcolor{orange}{0.822} & \textcolor{orange}{-} \\
     \textit{arima} && 0.814 & - \\
     \textcolor{orange}{\textit{hermes-thetam}} && \textcolor{orange}{0.808} & \textcolor{orange}{0.006} \\
     \textcolor{orange}{\textit{hermes-ets}} && \textcolor{orange}{0.792} & \textcolor{orange}{0.003} \\
     \textcolor{orange}{\textit{ets}} && \textcolor{orange}{0.786} & \textcolor{orange}{-} \\
     \textcolor{orange}{\textit{prophet}} && \textcolor{orange}{0.767} & \textcolor{orange}{-} \\
     \textit{lstm} && 0.767 & 0.045 \\
     \textit{stlm} && 0.742 & - \\
     \textit{tbats} && 0.745 & - \\
     \textbf{\textit{hermes-tbats}} && \textbf{0.739} & 0.003 \\
  \end{tabular}
 }
\label{tab:1000metricresults}
\end{table}

@@

\appendix

\section{M4 weekly dataset, Ensembling training and results}
